MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-17 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
biomart obj on Synapse while site is down

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", 
                host = "uswest.ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "percentage_gene_gc_content", "gene_biotype", "chromosome_name"),
                       filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
                       mart = mart)

>>>>

# Biomart down until April 20th maintenance
# Define biomart object
# mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", 
#                 host = "uswest.ensembl.org", # Ensembl Release 99 (January 2020)
#                 dataset = "hsapiens_gene_ensembl")
# 
# # Query biomart
# Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "percentage_gene_gc_content", "gene_biotype", "chromosome_name"),
#                        filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
#                        mart = mart)
Ensemble2HGNC = downloadFile("syn21907981")
